\section{Weak matrix elements}

This section briefly discusses our Weak Matrix element calculation.

\subsection{Calculation with point sources}

We wish to contract the following four quark operator, which via
the OPE describes the leading order box diagram for neutral meson
mixing,
\begin{equation}
C_{\mathfrak{O}_i}(t_i,0,t_f:t)^{LLL}=\sum_{x_i,x_f}^{V_{ND-1}} \bar{\Psi}^{f1}(x_f,t-t_f)\gamma_5 \Psi^{f2}(x,t-t_f) \mathfrak{O}(0) \bar{\Psi}^{f1}(x_f,t-t_i)\gamma_5 \Psi^{f2}(x,t-t_i).
\end{equation}
We put the operator at the point $(0,0)$ and have propagator solutions
at two different, well separated source positions $(0,t_f)$ and 
$(0,t_i)$.

In the standard model neutral kaons mix with a purely Vector-Axial
structure, so the operator is,
\begin{equation}
\mathfrak{O}_1(0) = \bar{\Psi}^{f1}(0)\gamma_\mu(1-\gamma_5)\Psi^{f2}(0)\bar{\Psi}^{f1}(0)\gamma_\mu(1-\gamma_5)\Psi^{f2}(0).
\end{equation}
Upon wick contraction we have,
\begin{equation}
\begin{aligned}
C_{\mathfrak{O}_1}(t_i,0,t_f:t)^{LLL}=\sum_{x_i,x_f}^{V_{ND-1}}
&\text{Tr}\bigg[
\gamma_5 ( \gamma_5 S(x_f,t-t_f) \gamma_5 )^{\dagger} \gamma_\mu ( 1 - \gamma_5 ) S(x_i,t-t_i)\\
&\:\:\:\:\:\gamma_5 ( \gamma_5 S(x_i,t-t_i) \gamma_5 )^{\dagger} \gamma_\mu ( 1 - \gamma_5 ) S(x_f,t-t_f)
\bigg]\\
-&\text{Tr}\bigg[ 
  \gamma_5 ( \gamma_5 S(x_f,t-t_f) \gamma_5 )^{\dagger} \gamma_\mu ( 1 - \gamma_5 ) S(x_i,t-t_i)
\bigg] \\
&\text{Tr}\bigg[ 
  \gamma_5 ( \gamma_5 S(x_i,t-t_i) \gamma_5 )^{\dagger} \gamma_\mu ( 1 - \gamma_5 ) S(x_f,t-t_f)
\bigg].
\end{aligned}
\end{equation}

In the asymptotic regime, we should have a plateau (in this example I use Kaons),
\begin{equation}
C_{\mathfrak{O}_1}(t_i,0,t_f:t)^{LLL} \lim{t_i<<t<<t_f} = < 0 | P | K >< K | \mathfrak{O}_1(0) | K > < K | P | 0 > e^{m_K (t_f - t_i ) }.  
\end{equation}
P here is a pseudoscalar meson operator.

\subsection{Calculation with walls}

The above discussion is not really how best to do the calculation, local sources
are noisy and often have poor overlap with the ground state. It is much more 
economical to use gauge-fixed wall sources at two well separated wall source
positions and move the operator's position.

In the code we only support the wall source computation, we also only compute,
\begin{equation}
\begin{aligned}
C_{\Gamma_1\Gamma_2}(t_i,t,t_f)^{WLW}=\sum_{x_i,x_f}^{V_{ND-1}}
&\text{Tr}\bigg[
\gamma_5 ( \gamma_5 S(x_f,t-t_f) \gamma_5 )^{\dagger} \Gamma_1 S(x_i,t-t_i)\\
&\:\:\:\:\:\gamma_5 ( \gamma_5 S(x_i,t-t_i) \gamma_5 )^{\dagger} \Gamma_2 S(x_f,t-t_f)
\bigg]\\
-&\text{Tr}\bigg[ 
  \gamma_5 ( \gamma_5 S(x_f,t-t_f) \gamma_5 )^{\dagger} \Gamma_1 S(x_i,t-t_i)
\bigg] \\
&\text{Tr}\bigg[ 
  \gamma_5 ( \gamma_5 S(x_i,t-t_i) \gamma_5 )^{\dagger} \Gamma_2 S(x_f,t-t_f)
\bigg].
\end{aligned}
\end{equation}
For all possible ($(NS\times NS)^2$) $\Gamma$s in our basis. This means that to
compute the full $V-A$ correlator, the combination,
\begin{equation}
C_{V_\mu,V_\mu}(t_i,t,t_f)^{WLW} - C_{A_\mu,A_\mu}(t_i,t,t_f)^{WLW}.
\end{equation}
Should be taken.

In general the following dirac structures also appear in the OPE.
\begin{equation}
V+A,\quad S+P ,\quad S-P ,\quad TT.
\end{equation}
And can be used to bound possible BSM scenarios which mix Kaons.
